Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
Minor

Additionally,
 the approach of specifying in a single codebase 
 parts of the structure, behaviour, and/or interaction 
 for a whole distributed system
 is also related to \emph{macroprogramming}~\cite{Casadei2023macro}
 and, in particular, to \emph{multi-tier programming} paradigm~\cite{DBLP:journals/csur/WeisenburgerWS20},
 where the deployment units for different tiers
(e.g., client and server tiers; or view, business logic, and data tiers)
are obtained by compilation or interpretation of a single codebase.

>>>>

Additionally,
 the approach of specifying in a single codebase 
 parts of the structure, behaviour, interaction 
 and/or other aspects of a whole distributed system
 is also related to \emph{macroprogramming}~\cite{Casadei2023macro}
 and, in particular, to \emph{multi-tier programming} paradigm~\cite{DBLP:journals/csur/WeisenburgerWS20},
 where the deployment units for different tiers
(e.g., client and server tiers; or view, business logic, and data tiers)
are obtained by compilation or interpretation of a single codebase.
